Online appendix for "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy

### 2021-04-17 manuscript/appendix.Rmd
Make target for appendix

---
title: 'Online appendix for "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy"'
short-title: 'Online appendix for "Who Cares About Crackdowns?"'
author:
- name: Suparna Chaudhry
  affiliation: Lewis & Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
- name: Marc Dotson
  affiliation: Brigham Young University
  url: https://marriottschool.byu.edu/directory/details?id=50683
  email: marc_dotson@byu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
date: "October 2, 2020"
title-page: false
published: 
git-repo: https://github.com/andrewheiss/who-cares-about-crackdown
reference-section-title: References
toc: true
appendix: true
---

>>>>

---
title: 'Online appendix for "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy"'
short-title: 'Online appendix for "Who Cares About Crackdowns?"'
author:
- name: Suparna Chaudhry
  affiliation: Lewis & Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
- name: Marc Dotson
  affiliation: Brigham Young University
  url: https://marriottschool.byu.edu/directory/details?id=50683
  email: marc_dotson@byu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
date: "April 17, 2021"
title-page: false
published: 
git-repo: https://github.com/andrewheiss/who-cares-about-crackdown
reference-section-title: References
toc: true
appendix: true
---
